Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-03-19 inst/surfing_jsa_rebuttal.tex

To the authors,

An interesting paper submitted, thank you. My only
real concerns are your actual comments related to the sport of
competitive surfing.

Firstly, some confusion as you initially state heats involve one or
two other competitiors. However, you begin the second paragraph in the
introduction with a statement saying 'up to four surfers', so which is
it?

\textcolor{blue}{We have removed the inconsistency (and made the text
  more precise) by rephrasing the introduction which now reads:
  ``Competitive surfing involves surfers competing against one {\em or
    more} other surfers in heats\ldots''}

@@

{\bf intent: }  WSL is the *professional* body organisation.

\subsection*{Male vs female competition issues}

34 surfers are for the mens competition.

\textcolor{blue}{We have clarified that we are studying the men's
  championship}

### 2022-03-19 inst/surfing_jsa.tex
referee: "is it up to four surfers"
referee: men's championship

\subsubsection*{Abstract}
Here we analyse competitive surfing, specifically the 2019 World Surf
League, using formal statistical methods.  We use generalized
Bradley-Terry likelihoods to assess a number of hypotheses of interest
to the surfing community.  Specifically, we quantify the dominance of
the top competitors using likelihood techniques, and go on to study
the ``Brazilian storm'' phenomenon using reified entities in two ways.
Firstly we assess the supposed Brazilian preference for beach break
and point break wave types; and secondly we consider results from the
perspective of tournament theory and test for competitors modifying
their strategy in the presence of compatriot rivals.  We quantify the
evidence for these commonly assumed features of contemporary
competitive surfing and suggest further avenues of research.

@@

Surfing is a popular and growing activity in terms of both
participation and viewing \citep{warshaw2010}.  Competitive surfing
involves surfers competing against one or two other surfers in heats
lasting 30-50 minutes \citep{booth1995}.  Points are awarded on a
10-point scale: each of five judges awards points to a surfer riding a
particular wave.  The World Surf League (WSL) is the main governing
body of surfing competitions \citep{wsl}.  The WSL conducts a world
tour in which the best ranked 34 surfers compete; in addition, at each
tour venue, two ``wildcard" surfers also enter the competition, who
are ignored here due to their generally poor performance and low
participation.

>>>>

\subsubsection*{Abstract}
Here we analyse competitive surfing, specifically the 2019 Men's World Surf
League, using formal statistical methods.  We use generalized
Bradley-Terry likelihoods to assess a number of hypotheses of interest
to the surfing community.  Specifically, we quantify the dominance of
the top competitors using likelihood techniques, and go on to study
the ``Brazilian storm'' phenomenon using reified entities in two ways.
Firstly we assess the supposed Brazilian preference for beach break
and point break wave types; and secondly we consider results from the
perspective of tournament theory and test for competitors modifying
their strategy in the presence of compatriot rivals.  We quantify the
evidence for these commonly assumed features of contemporary
competitive surfing and suggest further avenues of research.

@@

Surfing is a popular and growing activity in terms of both
participation and viewing \citep{warshaw2010}.  Competitive surfing
involves surfers competing against one or multiple other surfers in heats
lasting 30-50 minutes \citep{booth1995}.  Points are awarded on a
10-point scale: each of five judges awards points to a surfer riding a
particular wave.  The World Surf League (WSL) is the main governing
body of surfing competitions \citep{wsl}.  The WSL conducts a world
tour in which the best ranked 34 surfers compete; in addition, at each
tour venue, two ``wildcard" surfers also enter the competition, who
are ignored here due to their generally poor performance and low
participation.
